---
title: "Report for my project"
author: "Anqi Dai"
date: "`r format(Sys.Date(), '%Y-%m-%d')`"
output: html_document
---

### Load heritability data for four different methods: GSVA scores, PLAGE scores, singscores and z-scores.
```{r}
load("./data/resultg.RData")
resultg <- resultg
load("./data/resultp.RData")
resultp <- resultp
load("./data/results.RData")
results <- results
load("./data/resultz.RData")
resultz <- resultz
```

### Summary $h^2$ for each methods and output as csv files named summary* and make dataframe named data* to summary basic information for each methods
```{r,warning=FALSE}
#set output folder
outf="./"
summaryg <- c()
datag<-c()
for(i in 1:49){
  summaryg <- cbind(summaryg,resultg[[i]]$`V(G)/Vp`)
  datag<-rbind(datag,cbind(rep(names(resultg)[i],186),rownames(resultg[[1]]),
                           resultg[[i]]$`V(G)/Vp`,resultg[[i]]$n))
}
datag<-as.data.frame(datag)
colnames(datag)  <- c('tissue','pathway','hsquare','n')
rownames(summaryg) <- rownames(resultg[[1]])
colnames(summaryg)  <- names(resultg)
write.csv(summaryg,file=paste0(outf,"summaryg.csv"),quote=F,row.names=T,col.names=T)
print(paste0("file was saved at ",outf,"summaryg.csv"))

summaryp <- c()
datap<-c()
for(i in 1:49){
  summaryp <- cbind(summaryp,resultp[[i]]$`V(G)/Vp`)
  datap<-rbind(datap,cbind(rep(names(resultp)[i],186),rownames(resultp[[1]]),
                           resultp[[i]]$`V(G)/Vp`,resultp[[i]]$n))
}
datap<-as.data.frame(datap)
colnames(datap)  <- c('tissue','pathway','hsquare','n')
rownames(summaryp) <- rownames(resultp[[1]])
colnames(summaryp)  <- names(resultp)
write.csv(summaryp,file=paste0(outf,"summaryp.csv"),quote=F,row.names=T,col.names=T)
print(paste0("file was saved at ",outf,"summaryp.csv"))

summarys <- c()
datas<-c()
for(i in 1:49){
  summarys <- cbind(summarys,results[[i]]$`V(G)/Vp`)
  datas<-rbind(datas,cbind(rep(names(results)[i],186),rownames(results[[1]]),
                           results[[i]]$`V(G)/Vp`,results[[i]]$n))
}
datas<-as.data.frame(datas)
colnames(datas)  <- c('tissue','pathway','hsquare','n')
rownames(summarys) <- rownames(results[[1]])
colnames(summarys)  <- names(results)
write.csv(summarys,file=paste0(outf,"summarys.csv"),quote=F,row.names=T,col.names=T)
print(paste0("file was saved at ",outf,"summarys.csv"))

summaryz <- c()
dataz<-c()
for(i in 1:49){
  summaryz <- cbind(summaryz,resultz[[i]]$`V(G)/Vp`)
  dataz<-rbind(dataz,cbind(rep(names(resultz)[i],186),rownames(resultz[[1]]),
                           resultz[[i]]$`V(G)/Vp`,resultz[[i]]$n))
}
dataz<-as.data.frame(dataz)
colnames(dataz)  <- c('tissue','pathway','hsquare','n')
rownames(summaryz) <- rownames(resultz[[1]])
colnames(summaryz)  <- names(resultz)
write.csv(summaryz,file=paste0(outf,"summaryz.csv"),quote=F,row.names=T,col.names=T)
print(paste0("file was saved at ",outf,"summaryz.csv"))

```
The number of missing values for datag: `r sum(is.na(summaryg))`  
The number of missing values for datap: `r sum(is.na(summaryp))`  
The number of missing values for datas: `r sum(is.na(summarys))`  
The number of missing values for dataz: `r sum(is.na(summaryz))`  

### Order by mean $h^2$ (codes are hidden)
```{r,include=FALSE}
library("dplyr")
datag$hsquare<-as.numeric(as.character(datag$hsquare))
datag$n<-as.numeric(as.character(datag$n))
mmg <- datag %>% group_by(tissue) %>% summarise(m=mean(hsquare,na.rm = TRUE),n=mean(n,na.rm = TRUE))
b<-mmg %>% arrange(desc(m))
datag$tissue<-factor(datag$tissue,levels=as.character(b$tissue))
b <- datag %>% group_by(pathway) %>% summarise(m=mean(hsquare,na.rm = TRUE))
b<-b %>% arrange(desc(m))
datag$pathway<-factor(datag$pathway,levels=as.character(b$pathway))

datap$hsquare<-as.numeric(as.character(datap$hsquare))
datap$n<-as.numeric(as.character(datap$n))
mmp <- datap %>% group_by(tissue) %>% summarise(m=mean(hsquare,na.rm = TRUE),n=mean(n,na.rm = TRUE))
b<-mmp %>% arrange(desc(m))
datap$tissue<-factor(datap$tissue,levels=as.character(b$tissue))
b <- datap %>% group_by(pathway) %>% summarise(m=mean(hsquare,na.rm = TRUE))
b<-b %>% arrange(desc(m))
datap$pathway<-factor(datap$pathway,levels=as.character(b$pathway))

datas$hsquare<-as.numeric(as.character(datas$hsquare))
datas$n<-as.numeric(as.character(datas$n))
mms <- datas %>% group_by(tissue) %>% summarise(m=mean(hsquare,na.rm = TRUE),n=mean(n,na.rm = TRUE))
b<-mms %>% arrange(desc(m))
datas$tissue<-factor(datas$tissue,levels=as.character(b$tissue))
b <- datas %>% group_by(pathway) %>% summarise(m=mean(hsquare,na.rm = TRUE))
b<-b %>% arrange(desc(m))
datas$pathway<-factor(datas$pathway,levels=as.character(b$pathway))

dataz$hsquare<-as.numeric(as.character(dataz$hsquare))
dataz$n<-as.numeric(as.character(dataz$n))
mmz <- dataz %>% group_by(tissue) %>% summarise(m=mean(hsquare,na.rm = TRUE),n=mean(n,na.rm = TRUE))
b<-mmz %>% arrange(desc(m))
dataz$tissue<-factor(dataz$tissue,levels=as.character(b$tissue))
b <- dataz %>% group_by(pathway) %>% summarise(m=mean(hsquare,na.rm = TRUE))
b<-b %>% arrange(desc(m))
dataz$pathway<-factor(dataz$pathway,levels=as.character(b$pathway))
```

### Compare heatmaps across four methods
```{r,warning=FALSE,message=FALSE,fig.width = 20, fig.height = 20}
library(ComplexHeatmap)
library(circlize)
col_fun = colorRamp2(c(0,0.25, 0.5), c("blue","white","red"))
p1<-Heatmap(summarys,cluster_rows = FALSE,cluster_columns = FALSE,col = col_fun,
            name = "heritability for singscores",row_title = "KEGG Pathway", column_title = "singscores",
            row_names_gp = gpar(fontsize = 5) ,column_names_gp = gpar(fontsize = 6))
p2<-Heatmap(summaryz,cluster_rows = FALSE,cluster_columns = FALSE,col = col_fun,
            name = "heritability for z-scores",row_title = "KEGG Pathway", column_title = "z-scores",
            row_names_gp = gpar(fontsize = 5),column_names_gp = gpar(fontsize = 6))
p3<-Heatmap(summaryp,cluster_rows = FALSE,cluster_columns = FALSE,col = col_fun,
            name = "heritability for PLAGE scores",row_title = "KEGG Pathway", column_title = "PLAGE",
            row_names_gp = gpar(fontsize = 5),column_names_gp = gpar(fontsize = 6))
p4<-Heatmap(summaryg,cluster_rows = FALSE,cluster_columns = FALSE,col = col_fun,
            name = "heritability for GSVA scores",row_title = "KEGG Pathway", column_title = "GSVA",
            row_names_gp = gpar(fontsize = 5),column_names_gp = gpar(fontsize = 6))
htlist<- p1+p2+p3+p4
draw(htlist, column_title = "Tissues", column_title_gp = gpar(fontsize = 12))
```

### Calculate the correlation matrix between four methods using all the heritability data
```{r,warning=FALSE}
allg <- c()
for(i in 1:49){
  allg <- c(allg,as.vector(resultg[[i]]$`V(G)/Vp`))
}
allp <- c()
for(i in 1:49){
  allp <- c(allp,as.vector(resultp[[i]]$`V(G)/Vp`))
}
alls <- c()
for(i in 1:49){
  alls <- c(alls,as.vector(results[[i]]$`V(G)/Vp`))
}
allz <- c()
for(i in 1:49){
  allz <- c(allz,as.vector(resultz[[i]]$`V(G)/Vp`))
}
all<-cbind(allp,allg,alls,allz)
corall<-cor(all, method = "pearson", use = "complete.obs")
rownames(corall)=c("GSVA scores", "PLAGE scores", "singscores", "z-scores")
colnames(corall)=c("GSVA scores", "PLAGE scores", "singscores", "z-scores")
corall
```
